\clearpage

\section{SNR Estimator}

\begin{refsection}

\begin{tcolorbox}	
	\begin{tabular}{p{2.75cm} p{0.2cm} p{10.5cm}} 	
		\textbf{Header File}   &:& snr\_estimator\_*.h \\
		\textbf{Source File}   &:& snr\_estimator\_*.cpp \\
		\textbf{Version}	   &:& 20180313 (Andoni Santos)
	\end{tabular}
\end{tcolorbox}

\subsection*{Input Parameters}

\begin{table}[H]
	\centering
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Name}  		 & \textbf{Type}  & \textbf{Value}    	\\\hline
		Confidence     		 & double         & 0.95              	\\\hline
		measuredIntervalSize & int 			  & 1024				\\\hline
		windowType			 & WindowType     & Hamming			  	\\\hline
		segmentSize			 & int			  & 512					\\\hline
		overlapCount  		 & int			  & 256					\\\hline
%		LowestMinorant & double         & $1\times10^{-10}$ \\ \hline
	\end{tabular}
\end{table}

\subsection*{Input Signals}

\textbf{Number}: 1\\
\textbf{Type}: OpticalSignal or TimeContinuousAmplitudeContinuousReal

\subsection*{Output Signals}

\textbf{Number}: 1\\
\textbf{Type}: TimeDiscreteAmplitudeContinuousReal

\subsection*{Functional Description}

This block accepts one OpticalSignal or TimeContinuousAmplitudeContinousReal signal, estimates the signal-to-noise ratio for a given time interval and outputs an exact copy of the input signal. The estimated SNR value is printed to \textit{cout} after each calculation.  The block also writes a \textit{.txt} file reporting the estimated signal-to-noise ratio, a count of the number of measurements and the corresponding bounds for a given confidence level.

\subsection*{Theoretical Description}\label{snrcalc}
The SNR is calculated multiple times through the power spectral density of the signal over a given time interval. The multiple SNR measurements are then averaged and the confidence interval is established based on the observations.

The power spectrum is estimated through Welch's periodogram over a predefined interval size~\cite{john2007digital}. Using the power spectrum obtained from this sequence, the frequency interval containing the signal is estimated from the sampling rate, symbol rate and modulation type. This interval contains the power of both the signal and some of the white noise.

The power of a signal can be calculated from its power spectrum~\cite{john2007digital}:

\begin{equation}
P = \frac{1}{N} \sum_{n=0}^{N-1} {|x(n)|}^2 = \frac{1}{N^2} \sum_{k=0}^{N-1} {|X(k)|}^2
\end{equation}


By default, the noise is assumed to be AWGN with a given constant spectral density. Therefore, the power of the noise within the signal frequencies can be estimated from the rest of the noise spectrum.
The noise power is estimated from the integral of the spectrum in the area without signal, extrapolating for the total noise power in the spectrum. The signal power is obtained by integrating the spectrum within the signal's frequency interval, minus the corresponding superimposed noise, according to what was previously estimated. The power SNR is the ratio between these two values.

This value is saved and the process is repeated for every sequence of samples. The confidence interval is calculated based on the all the obtained SNR values~\cite{tranter2004principles}. The SNR value and confidence interval is saved to a text file.

%This block output signal is exactly equal to the input signal, to estimate SNR at any point in a given simulated system without interfering with it.

%The $\widehat{\text{BER}}$ is obtained by counting both the total number received bits, $N_T$, and the number of coincidences, $K$, and calculating their relative ratio:
%\begin{equation}
%\widehat{\text{BER}}=1-\frac{K}{N_T}.
%\end{equation}

%The upper and lower bounds, $\text{SNR}_\text{UB}$ and $\text{SNR}_\text{LB}$ respectively, are calculated using the Clopper-Pearson confidence interval.
%, which returns the following simplified expression for $N_T>40$~\cite{almeida2016continuous}:
%\begin{align}
%	\text{BER}_\text{UB}&=\widehat{\text{BER}}+\frac{1}{\sqrt{N_T}}z_{\alpha/2}\sqrt{\widehat{\text{BER}}(1-\widehat{\text{BER}})}+\frac{1}{3N_T}\left[2\left(\frac{1}{2}-\widehat{\text{BER}}\right)z_{\alpha/2}^2+(2-\widehat{\text{BER}})\right]\\
%	\text{BER}_\text{LB}&=\widehat{\text{BER}}-\frac{1}{\sqrt{N_T}}z_{\alpha/2}\sqrt{\widehat{\text{BER}}(1-\widehat{\text{BER}})}+\frac{1}{3N_T}\left[2\left(\frac{1}{2}-\widehat{\text{BER}}\right)z_{\alpha/2}^2-(1+\widehat{\text{BER}})\right],
%\end{align}
%where $z_{\alpha/2}$ is the $100\left(1-\frac{\alpha}{2}\right)$th percentile of a standard normal distribution.

\subsection*{Known Issues}\label{snrestissues}

This block currently only works with \textit{TimeContinuousAmplitudeContinuousReal} signals. It has also only been tested with the in-phase and quadrature components of an MQAM signal with M=4.
It also does not work correctly if the noise's power spectral density is high enough for the signal not to be detected (in the mentioned case, SNR < -10dB).



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% bibliographic references for the section ----------------------------
\clearpage
\printbibliography[heading=subbibliography]
\end{refsection}
\addcontentsline{toc}{subsection}{Bibliography}
\cleardoublepage
% ---------------------------------------------------------------------
